\chapter*{Campaign Pitch}\phantomsection\addcontentsline{toc}{chapter}{Campaign Pitch}
\DndDropCapLine{B}{\entryfont rave adventurers, welcome to the land of medieval Caledonia - nowadays Scotland! This is a world of mighty warriors, arcane magic, and legendary beasts, where the echoes of battle songs ring through ancient castles and the wind carries whispers of forgotten prophecies. Here, heroes are forged in the heat of battle, kings rule by sword and spell, and unseen forces stir beneath the surface of reality.}
\subsection*{Setting}
{\entryfont The year is 992 AD.

The Kingdom of Fife stands at the dawn of a new era. Prince Angus McFife, heir to the throne, is set to wed Lady Iona McDougall, daughter of the grandmaster of Crail - an alliance that promises to bring unity and strength to both realms. As nobles, warriors, and emissaries gather in the royal city of Dundee, festivities are in full swing. The great halls are filled with music, the forges burn bright, and the people of Fife celebrate a future of peace.

Yet, across the land, whispers of unease grow louder. Strange lights flicker in the deep woods. Hunters vanish without a trace, their weapons found shattered upon the ground. In the distant mountains, the cries of beasts long thought extinct echo through the valleys. Some dismiss it as mere superstition, while others fear that something stirs in the shadows - a force unseen, waiting for the right moment to strike.

For now, the focus remains on the grand wedding, a historic moment that could shape the fate of Fife for generations to come. But in a land of heroes and legends, fate has a way of calling even the most unlikely adventurers into the fire of destiny.}
\subsection*{What to Expect}
{\entryfont\begin{itemize}
	\renewcommand\labelitemi{\textbf{\textbullet}}
	\item \textbf{Diplomatic Relations}\\Navigate the shifting politics between the Kingdom of Fife, the Knights of Crail, and other powerful factions.
	\item \textbf{Travelling across the Kingdom}\\Explore the grand halls of Dundee, the towering citadel of Crail, and the mystical Land of Unicorns.
	\item \textbf{Dungeon Delving}\\Ancient ruins, forgotten tombs, and perilous crypts hide secrets lost to time.
	\item \textbf{Skill Challenges}\\Face puzzles, riddles, and contests of skill, from solving arcane mysteries to competing in grand tournaments.
	\item \textbf{High Fantasy, High Chaos}\\Expect epic battles, legendary weapons beyond mortal comprehension, and magical beasts like unicorns, dragons, as well as large goblin hordes.
	\item \textbf{Fife, but not as you know it}\\A world of dwarven ale-forges, barbarian clans, and technological advancements. But strange disappearances and eerie omens suggest that something is not quite right in the lands of Fife.
\end{itemize}}
\vfill\eject
\subsection*{Factions}
{\entryfont\paragraph*{Kingdom of Fife} The mighty realm of King Dundax \RoyalRoman{XIII} and Prince Angus McFife, lying in eastern Caledonia. Its capital, Dundee, was founded nearly a thousand years ago by the legendary hero Dundax, who shaped the foundation of this proud kingdom. Fife is a land of noble warriors, grand castles, and rich traditions, standing as a beacon of order and strength in a realm where magic and chaos often collide.}
\hfill\vspace*{-1.7\fontdimen6\font}\\
{\entryfont\paragraph*{Templar Knights of Crail} A storied brotherhood of warriors, founded by Prolon \RoyalRoman{I} in 450 AD. Renowned for their skill in battle and their legendary eagle-riding cavalry, the Knights once waged a brutal war against the principalities of Angus and Fyfdonia in 743 AD. After years of bloodshed, the war ended in unification, forging the modern Kingdom of Fife. The Knights remain an independent and powerful force, sworn to uphold honour and justice.}
\hfill\vspace*{-0.5\fontdimen6\font}\\
{\entryfont\paragraph*{Dwarves of Caledonia: Aberdeenshi \& Methven}\hfill\\Two great dwarven clans shape Caledonia, divided by their views on magic.

The Aberdeenshi Dwarves, dwelling beneath Aberdeen and Dundee, are legendary blacksmiths, binding magic to steel to forge unmatched weapons and armor.

The Methven Dwarves, living in the Mines of Methven in the western mountains of Fife, are alchemists and brewers, crafting powerful potions and their famed enchanted ale, rumored to grant visions of the future.

Though kin by blood, the two clans clash - steel versus alchemy, forge versus flask.}
\hfill\vspace*{-0.5\fontdimen6\font}\\
{\entryfont\paragraph*{Kingdom of Unst} A fierce barbarian kingdom on an island in the far north of Caledonia, Unst is a land of harsh winters, brutal martial training, and warriors forged in the fires of endless battle. Led by the legendary Hootsman, the warriors of Unst are as wild as the storms that rage across their shores. To them, strength is everything, and only the mighty deserve to rule. Many fear their warriors, but those who earn their respect find allies of unwavering loyalty.}
\hfill\vspace*{-0.5\fontdimen6\font}\\
{\entryfont\paragraph*{Lordship of Auchtertool} A realm where magic and technology intertwine, ruled by the enigmatic Mecha-Lord and his heir, the Robot Prince of Auchtertool. The lordship stands as a hub for artificers, forge clerics, and arcane engineers, where ancient spells fuel mechanical marvels. From towering war machines to enchanted automatons, Auchtertool is a land where the boundaries of science and sorcery blur, giving birth to creations both wondrous and terrifying.}
\hfill\vspace*{-0.5\fontdimen6\font}\\
{\entryfont\paragraph*{Elves of Dùn Èideann} South past the mist shrouded Firth of Forth lies the land of the elves. In the great city's ivory spires the Aeloria weave their enchantments in once mundane objects, while deep below the Umbrasil carve crystals and grow fungi. In the living groves across the region the Sylvani sculpture their spiral homes around ancient oaks and the Mistwalkers retrive treasures and riches from the often treacherous firth.}