\begin{DndMonster}[width=0.5\textwidth]{Corrupted Unicorn}
	\DndMonsterType{Large Undead, Chaotic Evil}
	
	% If you want to use commas in the key values, enclose the values in braces.
	\DndMonsterBasics[
		armor-class = {12},
		initiative	= +4,
		hit-points  = {\DndDice{10d10 + 20}},
		speed       = {50 ft.},
	]
	
	\renewcommand{\AbilityScoreSpacer}{~}
	\DndMonsterAbilityScores[
		str = 18,
		dex = 14,
		con = 15,
		int = 11,
		wis = 17,
		cha = 16,
	]
	
	\DndMonsterDetails[
%		saving-throws			= {CON +8, CHA +9},
%		skills					= {Insight +8, Intimidation +9, Perception +8},
%		damage-vulnerabilities	= {Cold},
		damage-resistances		= {Necrotic},
		damage-immunities		= {Poison},
		condition-immunities	= {Charmed, Paralyzed, Poisoned},
%		gear					= {Leather Armor, Light Crossbow, Scimitar},
		senses					= {Darkvision 60 ft., Passive Perception 13},
		languages				= {-},
		challenge				= 3,
		proficiency-bonus		= +2,
	]
	
	\DndMonsterSection{Traits}
    \DndMonsterAction{Charge}
	If the unicorn moves at least 20 feet straight toward a target and then hits it with a horn attack on the same turn, the target takes an extra \DndDice{2d8} Piercing damage. If the target is a creature, it must succeed on a DC 14 Strength Saving Throw or be knocked prone.
    
	\DndMonsterAction{Magic Resistance}
	The unicorn has advantage on saving throws against spells and other magical effects.
	
	\DndMonsterAction{Magic Weapons}
    The unicorn's weapon attacks are magical.
	
	\DndMonsterAction{Undead Nature}
	The unicorn doesn't require food, air, drink, or sleep.
	
	\DndMonsterSection{Actions}
	\DndMonsterAction{Multiattack}
	The unicorn makes two attacks: one with its hooves and one with its horn.
	
	\DndMonsterAttack[
		name			= Hooves,
		distance		= melee,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +6,
		reach			= 5,
%		range			= 20/60,
		targets			= one target,
		dmg				= \DndDice{2d6 + 4},
		dmg-type		= Bludgeoning,
%		plus-dmg		= \DndDice{1d6},
%		plus-dmg-type	= Poison,
%		or-dmg			= \DndDice{1d20 + 2},
%		or-dmg-when		= {},
%		extra			= {},
	]
	
	\DndMonsterAttack[
		name			= Horn,
		distance		= melee,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +6,
		reach			= 5,
%		range			= 20/60,
		targets			= one target,
		dmg				= \DndDice{1d8 + 4},
		dmg-type		= Piercing,
%		plus-dmg		= \DndDice{1d6},
%		plus-dmg-type	= Poison,
%		or-dmg			= \DndDice{1d20 + 2},
%		or-dmg-when		= {},
%		extra			= {},
	]
	
	\DndMonsterAction{Teleport (1/Day)}
	The unicorn magically teleports itself and up to three willing creatures it can see within 5 feet of it, along with any equipment they are wearing or carrying, to a location the unicorn is familiar with, up to 1 mile away.
	
	\DndMonsterSection{Spells}
	\begin{DndMonsterSpells}
		\item[Innate Spellcasting] The unicorn's innate spellcasting ability is Charisma (spell save DC 13, +5 to hit with spell attacks). The unicorn can innately cast the following spells, requiring no components:
		\DndInnateSpellLevel{Detect Evil and Good, Pass without Trace, Sapping Sting}
		\DndInnateSpellLevel[1]{Cause Fear, False Life, Ray of Sickness}
	\end{DndMonsterSpells}
	
	\DndMonsterSection{Bonus Actions}
	\DndMonsterAction{Memento Mori (3/Day)}
	The unicorn touches another creature with its horn. The sound of a dolorous bell fills the air around it for a moment. The target must succeed on a DC 13 Wisdom saving throw or take 1d8 Necrotic damage. If the target is missing any of its\\Hit Points, it instead takes 1d12 Necrotic damage.
\end{DndMonster}