\begin{DndMonster}[width=0.5\textwidth]{Festival Dragon}
	\DndMonsterType{Large Construct, neutral good}
	
	% If you want to use commas in the key values, enclose the values in braces.
	\DndMonsterBasics[
		armor-class = {16},
		hit-points  = {\DndDice{9d10 + 36}},
		speed       = {20 ft.},
	]
	
	\renewcommand{\AbilityScoreSpacer}{~}
	\DndMonsterAbilityScores[
		str = 7,
		dex = 7,
		con = 18,
		int = 8,
		wis = 18,
		cha = 20,
	]
	
	\DndMonsterDetails[
		saving-throws = {CON +8, CHA +9},
		skills = {Insight +8, Intimidation +9, Perception +8},
		%damage-vulnerabilities = {cold},
		%damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
		%damage-immunities = {poison},
		senses = {Passive Perception 18},
		%condition-immunities = {poisoned},
		languages = {-},
		challenge = -,
		proficiency-bonus = +4,
	]
	
	\DndMonsterSection{Traits}
    \DndMonsterAction{Operative Mastery}
    The Festival Dragon must be operated by a group of at least 6 people. If the Festival Dragon is operated by a properly trained performing team, its AC is increased by 2 and gains a bonus of +4 to each melee attack and damage roll.
    
	\DndMonsterAction{Non-Lethal Attacks}
	Each attack the Festival Dragon makes is considered non-lethal
	
	\DndMonsterAction{Friendly Nature}
    The Festival Dragon is usually friendly towards children and only chases them away, unless they get too greedy.
	
	\DndMonsterSection{Actions}
	\DndMonsterAction{Multiattack}
	The Festival Dragon makes one Claw Attack and one Bite or Tail Attack.
	
	\DndMonsterAttack[
		name=Claw,
		distance=melee, % valid options are in the set {both,melee,ranged},
		%type=weapon, %valid options are in the set {weapon,spell}
		mod=-2,
		reach=5,
		%range=20/60,
		targets=one target,
		dmg=\DndDice{1d4 - 2},
		dmg-type=slashing,
		%plus-dmg=\DndDice{1d6},
		%plus-dmg-type=poison,
		%or-dmg=,
		%or-dmg-when=,
		extra={ (minimum of 1 damage)},
	]
	
	\DndMonsterAttack[
		name=Bite,
		distance=melee, % valid options are in the set {both,melee,ranged},
		%type=weapon, %valid options are in the set {weapon,spell}
		mod=-2,
		reach=5,
		%range=20/60,
		targets=one target,
		dmg=\DndDice{1d6 - 2},
		dmg-type=piercing,
		%plus-dmg=\DndDice{1d6},
		%plus-dmg-type=poison,
		%or-dmg=,
		%or-dmg-when=,
		extra={ (minimum of 1 damage)},
	]
	
	\DndMonsterAttack[
		name=Tail,
		distance=melee, % valid options are in the set {both,melee,ranged},
		%type=weapon, %valid options are in the set {weapon,spell}
		mod=-2,
		reach=20,
		%range=20/60,
		targets=one target,
		dmg=\DndDice{1d6 - 2},
		dmg-type=bludgeoning,
		%plus-dmg=\DndDice{1d6},
		%plus-dmg-type=poison,
		%or-dmg=,
		%or-dmg-when=,
		extra={ (minimum of 1 damage)},
	]
	
	\DndMonsterAction{Breath Weapon (Recharge 5 Rounds)}
	Each creature in a 30ft. long, 5 ft. wide line must make a DC16 Dexterity Saving Throw or are instantly out of the Dragon's Gold game.
	
	\DndMonsterSection{Reactions}
	\DndMonsterAction{Automated Construct}
	The Festival Dragon can make one attack of opportunity with each of its front limbs, mouth, and tail.
\end{DndMonster}