\actpart{A Royal Wedding in Dundee}% Name of Act
	{}% Background Picture
	{0cm}% X-Shift
	{0cm}% Y-Shift
	{height=\paperheight}% Graphics-Options (height, width)
	{Act01}% Short-Handle
	{test}% URL
	{test}%	Image-Name
	{test}%	Artist

\DndDropCapLine{T}{\entryfont he campaign begins in the city of Dundee, a bustling metropolis in the heart of the Kingdom of Fife. The city is in the throes of grand celebration for the wedding of Prince Angus McFife and Lady Iona McDougall. Read aloud or paraphrase:}

\begin{DndReadAloud}
	As your party crests the final hill, the sprawling city of Dundee comes into view, its towering stone walls adorned with banners of blue and gold. The air buzzes with the sounds of celebration - cheering crowds, the lively strains of music, and the toll of bells from the grand citadel in the heart of the city.
	
	The streets are alive with bustling merchants, performers, and revellers from across the kingdom, all eager to witness the union that promises to bring peace and prosperity to the land.
\end{DndReadAloud}

\section*{The Braided Unicorn}\phantomsection\addcontentsline{toc}{section}{The Braided Unicorn}
{\entryfont Nestled in the heart of Dundee, The Braided Unicorn is a sturdy stone-built inn with a weathered slate roof and timber beams, exuding a timeless charm. Above the heavy oak door hangs a beautifully carved wooden sign of a proud unicorn, its mane braided with intricate patterns, as though prepared for some ancient, regal ceremony.

Inside, the air is filled with the scent of roasted meat, strong ale, and a hint of peat smoke. A massive hearth dominates the room, its fire crackling merrily. Above the fireplace hangs an ancient great axe, rumored to have belonged to the current owner's great-grandfather.

The tavern is run by Borin Stouthammer, a stout, no-nonsense mountain dwarf with a braided iron-grey beard and a voice like rolling thunder. He keeps a keen eye on patrons from behind the polished oak bar, where rows of wooden tankards and whisky casks line the walls. Borin is quick to laugh but quicker to enforce his rules.

At the entrance, a small board proudly displays "The Braided Unicorn's House Rules":
\begin{itemize}
	\item "Nae brawling near the bar"
	\item "If ye break it, ye buy it"
	\item "Sing in tune - or buy a round for the house"
\end{itemize}

Up a creaky staircase, cozy guest rooms await with clean beds, thick quilts, and sturdy locks on the doors - perfect for a night's rest during the city's celebrations.}
{\entryfont \paragraph*{Rumours} As the party mingles, a successful DC 12 Perception (hearing) check reveals the low murmur of an intense, anxious conversation coming from a nearby table.

The source is a group of five villagers, mostly hunters and woodsfolk, huddled close and speaking in hurried, hushed tones. Their expressions range from bewilderment to dread, and the table has several empty mugs.
\begin{itemize}
	\item \textit{"I tell ye, they weren't natural unicorns - one of 'em just stared at me, eyes black as pitch."}
	\item \textit{"Aye, and those bodies... distorted they were, like something twisted the poor beasts before killing them."}
	\item \textit{"Tis nae normal wounds! Mauled, but not like any predator I've ever seen."}
	\item \textit{"It's a plague, I say. A rabid curse! Something's got into the beasts and it's spreadin'."}
\end{itemize}
The group initially looks wary but opens up if the party approaches with care (DC 15 Persuasion check, or simply buying them a round of drinks).
\begin{itemize}
	\item They describe unicorn sightings in the nearby Dundee woods, where normally noble and peaceful unicorns have been seen acting strangely - charging madly, baring teeth, and collapsing mid-gallop.
	\item Several distorted corpses of animals (and one local hunter) have been found either mauled to death or show terrifying piercing wounds.
	\item Some whisper of a "rabid curse" or a spreading sickness. Others suggest something terrifying is lurking in the woods, frightening even the unicorns.
\end{itemize}}

{\entryfont \paragraph*{Gambling Station} At the far side of the common room, a corner is dedicated to a large, well-worn oak table surrounded by mismatched chairs. Above it hangs a cracked wooden sign with the words \textbf{"Fortune's Folly"} scrawled in faded paint. The table is always surrounded by locals, travelers, and a rotating cast of suspiciously smug regulars.

Borin Stouthammer has no patience for cheaters but allows gambling as long as it doesn't disrupt the tavern. The games played here are deceptively simple, promising quick coin - a fool's trap, as the locals say.

Players can engage with Arlen, a half elf with nimble fingers and a sharper tongue, and Breeza, a halfling dressed in flashy silks, to try their fortune in varying games:

\subparagraph*{Dice Game}
A player makes contested Deception and Insight Checks against Breeza (Breeza's Deception vs. Player's Insight and Breeza's Insight vs. Player's Deception).  The winner of each round gets 2 points to their score. If Breeza and the player tie both rolls or both win one roll each, each player gets 1 point. The first player reaching 10 points in total wins the game.

\noindent\textbf{Breeza's Cheating.} Breeza (Deception +7, Insight +5) can use Arlen as a spy gaining a +5 to her Insight rolls. Players can realize that they are cheated with a successful DC 15 (-2 for each time Breeza used Arlen to cheat) Insight Check.

\subparagraph*{The Everyman's Fireball}
Tiny, wooden objects (HP 10, AC 9, immobile) are placed on the far side of the table. Each player takes a mouthful of alcohol and spits through a flame\linebreak
\vspace*{-2.5\fontdimen6\font}\hfill\\\begin{tabular}{p{0.2\textwidth}p{0.2325\textwidth}}
	\hspace*{-0.5em}\begin{tabular}[t]{p{0.2\textwidth}}
		\vspace*{0.3em}\begin{DndTable}[header=Alcoholic Drinks]{lc}
			\textbf{Drink}	& \textbf{Strength}	\\
			Weak Beer		& 1					\\
			Regular Beer	& 2					\\
			Wine			& 4					\\
			Strong Wine		& 6					\\
		\end{DndTable}
	\end{tabular}
	&
	\vspace*{0.8em}\begin{tabular}[t]{p{0.2325\textwidth}}
		{\noindent\entryfont placed between the player and the object. Before "attacking" the object, a player must make a DC 12 Dexterity roll to not burn themselves, taking \DndDice{1d4 - 1} fire damage on a failed save. The player\linebreak}
	\end{tabular}
\end{tabular}
\vspace*{-1.6\fontdimen6\font}\hfill\\then makes a ranged attack (DEX, -4 to hit; additional -2 to hit if player failed DEX save) against the wooden object, dealing \DndDice{1d6} fire damage, but not more than the drink's strength, on a hit. After each round the objects AC and the Dexterity DC increases due to the effect the drinks have on the contestants:
\begin{itemize}
	\item Objects AC: + (Drink Strength / 3) rounded down
	\item Dexterity DC: + (Drink Strength / 2) rounded down
\end{itemize}
The first to destroy the wooden object wins the game - the game is considered a tie if both are destroyed at the same time.

\noindent\textbf{Arlen's Cheating.} If Arlen (DEX +5) hits the object or nearly misses it (AC - 3), Breeza activates a contraption that will lit up the idol dealing an additional \DndDice{1d4} fire damage to the object. A DC 17 (- amount of additional damage dealt) Insight Check reveals this cheating mechanism.
}

\subsection*{An Ape-napping}
{\entryfont As the party makes their way to exit the Braided Unicorn tavern, the door bursts open with a loud \textbf{CRASH}, nearly unhinging from its frame - The party member nearest to the door must succeed on a DC 15 Dexterity Saving Throw or takes 1 bludgeoning damage from the swung open door and is knocked prone.}

\begin{DndReadAloud}
	The door slams open with a thunderous \textbf{BANG}, silencing the tavern as a figure of regal authority strides in. A grand knight, his armour polished to a mirror-like gleam and adorned with the coat of arms of Crail, surveys the room. His breath is laboured, but his presence is unshaken, exuding an aura of command.

	\textit{"WHERE are my men?!"} he mutters, more to himself than anyone else, his voice tinged with frustration and urgency.

	His eyes settle on you, narrowing for a moment as if weighing your worth. Then, stepping forward with purpose, his voice booms with authority, yet carries a regal, almost poetic cadence:

	\textit{"You there! Adventurers! I see the fire of duty in your eyes. Will you rise to the occasion, as proud sons and daughters of Dundee? A task most urgent calls, and your valour will be met with rewards worthy of your bravery. What say thee?"}
\end{DndReadAloud}

{\noindent\entryfont Should the party express their willingness to assist, the Grandmaster will give them the details of their noble task to recover the prized ape, Bobo.}

\begin{DndQuestHook}[width=0.5\textwidth - 4pt]{Rescue Bobo}
	\DndQuestHookBasics[
		location = {The Braided Unicorn Tavern, Dundee},
		quest-giver = {Ser Proletius, Grandmaster of the Knights of Crail},
		objective = {Retrieve Prince Angus McFife's stolen pet ape, Bobo, from a bandit camp in the north-eastern woods near Dundee.},
	]
	
	{\noindent\entryfont If the party succeeds on a Survival (DC 13) check, they find signs of the camp - broken branches, footprints, and scattered food - leading them toward their destination. If they fail, they instead encounter a \hyperref[monster:BanditScout]{\LinkFont{Bandit Scout}} accompanied by two \hyperref[monster:Mastiff]{\LinkFont{Mastiffs}}. The scout attempts to fight or flee, sending one mastiff back to the camp to warn the bandits. If the scout is killed, the party can find a map to the camp on his body.

		As the party approaches the camp, they find it surrounded by several traps. A Falling Net Trap is hidden among the foliage and if triggered, the net restrains the target, and a \hyperref[monster:Bandit]{\LinkFont{Bandit}} and a \hyperref[monster:Mastiff]{\LinkFont{Mastiff}} emerge to attack. The mastiff may be sent back to warn the camp if it survives. The camp is also rigged with Warning Bell Traps. If triggered, the loud sound alerts the entire camp.

		Inside the bandit camp, the party finds two \hyperref[monster:Bandit]{\LinkFont{Bandits}} and two \hyperref[monster:Mastiff]{\LinkFont{Mastiffs}} near a wooden cage containing Bobo, the stolen pet ape. If the camp is alerted - whether by a bandit's mastiff or a warning bell - additional reinforcements arrive after two rounds: a \hyperref[monster:BanditScout]{\LinkFont{Bandit Scout}}, a \hyperref[monster:Bandit]{\LinkFont{Bandit}} and another \hyperref[monster:Mastiff]{\LinkFont{Mastiff}} - if not killed before.

		The party has options for non-lethal approaches. They can attempt to infiltrate the camp, bribe the bandits, or use stealth to avoid combat. Alternatively, the party can attempt to free Bobo quietly or with force, though loud actions will attract attention.

		Bobo, frightened but alive, is in a sturdy cage (Sleight of Hand DC 15 to lockpick with thieves' tools), and the party can calm him with food or gentle handling (Animal Handling DC 13) to ensure a smooth rescue.
	}
	
	\DndQuestRewards{Upon successfully retrieving Bobo, the party receives the following rewards from King Dundax \RoyalRoman{XIII} and Prince Angus McFife:}
	{%
		{Heroic Inspiration}{}%
		{Coupon for the Wedding Festival}{%
			Each character is given a coupon, redeemable at the festival grounds for one of the following:
			\begin{itemize}
				\item A free round of the Tree Game or Dragon's Gold games
				\item A hearty free meal at one of the many stalls
			\end{itemize}
		}%
		{Private Lodging}{As a further token of gratitude, the party is given private lodging at The Braided Unicorn, rather than having to sleep in the communal quarters. This gesture signifies their growing status in Dundee and ensures them a more comfortable stay during the wedding festivities.}
		{Tournament Entry Voucher}{This voucher allows participation in the prestigious Wedding Tourney}%
		{LEVEL-UP}{At the end of the session}
	}%
\end{DndQuestHook}
	
{\entryfont\noindent When the adventurers deliver Bobo to the commanders' tent, King Dundax \RoyalRoman{XIII}, Prince Angus McFife, and Ser Proletius express their joy and gratitude. After awarding the promised rewards, Ser Proletius will single out a barbarian, fighter, ranger, or rogue (if available) in the group by giving them the Tournament Entry Voucher and set them up for a personal challenge.}

\begin{DndReadAloud}
	Ser Proletius lips curl into a confident grin. \textit{"I challenge you to enter the Wedding Tournament. Should you reach the Jousting final, regardless of the outcome, I shall reward you with a magic item from my personal possession. But should you fail..."} He pauses, letting the moment hang in the air. \textit{"You shall join me during the wedding ceremony to sing the anthem of Crail, a song of honour, glory, and tradition."}
\end{DndReadAloud}

{\entryfont\noindent If the player successfully reached the final of the Jousting Tournament they can choose between the \textbf{Cast-Off Armour} (the armour-type can be chosen by the player) or the \textbf{Shield of Expression}.

If they win the final, Ser Proletius also allows the players to fly over the city of Dundee with the mighty Eagles of Crail.}

\begingroup
	\DndSetThemeColor[PhbLightGreen]
	\begin{DndComment}{Cast-Off Armour}
		\textit{Armour (light, medium, or heavy), common}\\
		You can doff this armour as an action.
	\end{DndComment}
	\begin{DndComment}{Shield of Expression}
		\textit{Armour (shield), common}\\
		The front of this shield is shaped in the likeness of a face. While bearing the shield, you can use a bonus action to alter the face's expression.
	\end{DndComment}
\endgroup

\input{parts/act01_chapters/ch01_Wedding_Fair}
\input{parts/act01_chapters/ch02_Wedding_Tourney}
\input{parts/act01_chapters/ch03_Wedding_Ceremony}
\input{parts/act01_chapters/ch04_Unicorn_Invasion_of_Dundee}