\actpart{Knigths of Crail}% Name of Act
	{}% Background Picture
	{}% X-Shift
	{}% Y-Shift
	{}% Graphics-Options (height, width)
	{}% Short-Handle
	{}% URL
	{}%	Image-Name
	{}%	Artist
	
\DndDropCapLine{S}{\entryfont moke drifts across the river, curling into the midday sky as Dundee burns, its once-proud towers now crumbling beneath Zargothrax's unholy dominion. Across the water, the city is lost - no voices call for help, no banners of resistance remain. The dead walk its streets, and whatever horrors the sorcerer has unleashed are left to fester in the ruins.}

{\entryfont On this side of the River Tay, the people who escaped are safe for now. The bridge's destruction has reverted the river into the impassable obstacle it once was. None can say what dark designs Zargothrax still has or when his forces will further spread their corruption. Time is running short, and there is no room for hesitation. Angus McFife and Ser Proletius stand at the ready, their expressions grim yet resolute. If there is any hope of striking back, an army must be raised. The knights of Crail must be called to war.}

\begin{DndReadAloud}
	Angus McFife breaks the silence first, his voice firm: \textit{"We cannot let this happen to the rest of Fife. Zargothrax must be stopped. But we are too few - charging back into battle now would be suicide. We need an army."} He turns to you, his expression unwavering. \textit{"The Knights of Crail are our best hope. You must go to the Citadel and call them to war."}

Ser Proletius nods, his gaze fixed on the few people who escaped the besieged city. \textit{"Angus and I will remain here - helping the survivors. Send the Great Eagles back to us when you arrive at the citadel."} He reaches into his pocket and retrieves a small token, pressing it into your hand. The metal is cool to the touch, marked with the sigil of Crail. \textit{"Show this to the quartermaster, and he will know I sent you."}

	Angus places a firm hand on your shoulder. \textit{"Go now. And do not fail."}
\end{DndReadAloud}

\begin{DndOptionalRule}{Restless Advancement}\label{or:RestlessAdvancement}%
	Even though the players earned a Level-Up after escaping the besieged city of Dundee, you may choose to withhold the benefits of a Long Rest at this time, as the urgency of the situation presses on. This rule reinforces the relentless pace of their flight and the desperate need to secure aid for the survivors.

	Despite not resting, players still gain all new features, spell slots, and increased hit points associated with their level-up. However, any previously expended resources, such as hit dice, spell slots, and class abilities that recharge on a Long Rest, remain unavailable until the party finds a true moment of respite.
\end{DndOptionalRule}

{\noindent\entryfont Emboldened by Angus McFife's unwavering words, the player he addresses feels a surge of courage and determination, gaining \DndDice{1d8 + 3} Temporary Hit Points. Before the party departs, Ser Proletius kneels in solemn prayer, his voice a soft murmur that calls upon divine strength. A gentle, radiant energy flows through the group, mending wounds and steadying resolve - if the optional rule is in play, each member of the party regains \DndDice{2d8 + 3} Hit Points.

Lastly, Ser Proletius hands over a detailed map of Eastern Caledonia, its markings clear and precise, providing guidance through the treacherous journey to the Citadel of Crail.}

\section*{Travelling Rules}\phantomsection\addcontentsline{toc}{section}{Travelling Rules}

\input{parts/act02_chapters/ch01_Way_of_Tay}
\input{parts/act02_chapters/ch02_Citadel_of_Crail}