\begin{DndMonster}[width=0.5\textwidth]{Vrock\phantomsection\addcontentsline{toc}{section}{Vrock}\label{monster:Vrock}}
	\DndMonsterType{Large Fiend (Demon), Chaotic Evil}
	
	% If you want to use commas in the key values, enclose the values in braces.
	\DndMonsterBasics[
		armor-class = {15 (Natural Armor)},
		initiative	= +2,
		hit-points  = {\DndDice{16d10 + 64}},
		speed       = {40 ft., Fly 60 ft.},
	]
	
	\renewcommand{\AbilityScoreSpacer}{~}
	\DndMonsterAbilityScores[
		str = 17,
		dex = 15,
		con = 18,
		int = 8,
		wis = 13,
		cha = 8,
	]
	
	\DndMonsterDetails[
		saving-throws			= {DEX +5, WIS +4, CHA +2},
		skills					= {Acrobatics +6, Perception +5, Stealth +8},
%		damage-vulnerabilities	= {Cold},
		damage-resistances		= {Cold, Fire, Lightning},
		damage-immunities		= {Poison},
		condition-immunities	= {Poisoned},
%		gear					= {Leather Armor, Light Crossbow, Scimitar},
		senses					= {Darkvision 120 ft., Passive Perception 11},
		languages				= {Abyssal, Telepathy 120 ft.},
		challenge				= 6,
		proficiency-bonus		= +3,
	]
    
	\DndMonsterSection{Traits}
	\DndMonsterAction{Demonic Restoration}
	If the Vrock dies outside the Abyss, its body dissolves into ichor, and it gains a new body instantly, reviving with all its Hit Points somewhere in the Abyss.
	
	\DndMonsterAction{Magic Resistance}
	The Vrock has Advantage on saving throws against spells and other magical effects.
	
	\DndMonsterSection{Actions}
	\DndMonsterAction{Multiattack}
	The Vrock makes two Shred attacks.
	
	\DndMonsterAttack[
		name			= Shred,
		distance		= melee,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +6,
		reach			= 5,
%		range			= 20/60,
		targets			= one target,
		dmg				= \DndDice{2d6 + 3},
		dmg-type		= Piercing,
		plus-dmg		= \DndDice{3d6},
		plus-dmg-type	= Poison,
%		or-dmg			= \DndDice{1d20},
%		or-dmg-when		= {},
%		extra			= {},
	]
	
	\DndMonsterSavingThrowEffect[
		name		= Spores (Recharge 6),
		save_skill	= Constitution,
		save_dc		= 15,
		targets		= {each creature in a 20-foot Emanation originating from the Vrock},
		failure		= {The target has the Poisoned condition and repeats the save at the end of each of its turns, ending the effect on itself on a success. While Poisoned, the target takes \DndDice{1d10} Poison damage at the start of its turns. Emptying a flask of Holy Water on the target ends the effect early.},
	]
	
	\DndMonsterSavingThrowEffect[
		name		= Stunning Screech (1 / Day),
		save_skill	= Constitution,
		save_dc		= 15,
		targets		= {each creature in a 20-foot Emanation originating from the Vrock (demons succeed automatically)},
		failure		= {\DndDice{3d6} Thunder damage, and the target has the Stunned condition until the end of the vrock's next turn.},
	]
\end{DndMonster}