\chapter*{Auchtertool}\stepcounter{chapter}\phantomsection\addcontentsline{toc}{chapter}{Auchtertool}
\DndDropCapLine{A}{\entryfont uchtertool is a city caught mid-transformation, where ancient stonework strains under the weight of a young and imperfect technological revolution. The foundations of its buildings are old-gray, weathered stone blocks laid generations ago - but they have been aggressively "improved" with exposed gears, rotating pistons, copper piping, and clanking lift-cranes bolted on wherever space allowed. The result is neither elegant nor fully stable: mechanisms grind loudly, steam hisses from ill-fitted valves, and the constant tick-tick-tick of clockwork fills the air like an anxious heartbeat.}

{\entryfont Crude mechanical constructs roam the streets in great numbers, each built for a specific task - hauling cargo, sweeping streets, delivering messages, or enforcing order - but few perform flawlessly. Some walk directly into walls and continue pushing as if confused, others spin endlessly in place, and a fair number simply collapse in showers of sparks and smoke. These failures are closely shadowed by Forge Clerics: robed engineers carrying tools, clipboards, and arcane measuring devices. Some eagerly jot notes and issue corrections; others hurriedly attempt repairs while pretending nothing is wrong; and a few, upon witnessing a particularly public malfunction, quietly duck into alleyways to avoid being associated with the embarrassment.}

\begin{DndReadAloud}
	As you enter Auchtertool, the sound hits you first: clanking metal, grinding gears, and the hiss of escaping steam echoing off stone walls. Buildings of gray rock loom over the streets, their sides bristling with bolted-on machinery that looks only mostly under control.

	A squat, barrel-shaped robot trundles past you, dragging a broom nearly twice its size. It sweeps enthusiastically for several seconds - then abruptly veers left and smacks directly into a wall. The robot pauses. Its eyes flicker. It reverses... and immediately drives into the same wall again, harder this time.

	"Ah. Yes. That's... new", mutters a nearby Forge Cleric, hastily scribbling notes while another one pretends not to see anything and casually walks in the opposite direction.

	Suddenly, the robot emits a cheerful chime, spins around, and begins sweeping the air, scattering dust directly onto a well-dressed passerby. The passerby sighs with long-suffering patience, while the robot proudly declares in a crackling voice:
	
	"CLEANING SUCCESSFUL. ENVIRONMENT IMPROVED."

	Above it all, towering at the city's center, rises a massive cathedral of stone and steel.
\end{DndReadAloud}
\vfill\eject
\section*{The Grand Cathedral}\phantomsection\addcontentsline{toc}{section}{The Grand Cathedral}
{\entryfont At the city's heart rises the Grand Cathedral, once devoted to forgotten gods whose names no one now remembers. Its soaring spires remain intact, but its purpose has been utterly transformed. The altar halls have become forges and laboratories, and enormous mosaic windows depict not saints or angels, but towering robots, perfect gear assemblies, and radiant machines bathed in golden light. Innovation itself is worshipped here, and mechanization has taken on a holy significance. From this repurposed cathedral, the Mecha-Lord and the Robot Prince of Auchtertool rule, blending political authority with technological doctrine, proclaiming that perfection is not inherited - but engineered.}

\begin{DndReadAloud}
	The moment you step inside the cathedral, the noise of the city dulls into a controlled, reverent hum. The vast hall stretches upward into shadow, its ancient stone arches reinforced with steel ribs and humming conduits. Light pours through immense mosaic windows overhead, casting shifting patterns of gold, crimson, and brass across the floor - images of perfected machines, flawless gears, and towering constructs replacing the saints of an older faith.

	Unlike the streets outside, the constructs here move with measured precision. Tall, elegant guardians of polished steel stand at key points along the nave, their movements smooth, their optics calmly tracking every motion. They radiate quiet authority, ensuring peace and order without menace. Between them, Forge Clerics and Artificers work at long tables arranged where pews once stood. Arcane tools glow softly as runes are etched into metal cores, cables are fused with spellcraft, and mechanical hearts are tested with pulses of light and energy. The air smells of incense, hot metal, and ozone.

	At the far end of the cathedral, where an altar once rose, stands something immense.

	A colossal construct towers more than fifteen feet high, its armoured form partially embedded into the cathedral itself. Thick cables and rune-etched conduits run from its body into the surrounding walls and machines, as though the building exists only to sustain it. This is not merely a machine - it is a presence. You feel it pressing against your thoughts, heavy and deliberate, as if your minds are being calmly observed, weighed, and catalogued.

	Before the construct lies a recessed basin filled with liquid metal, glowing gold-red like molten sunlight. Within it, massive interlocking golden loops rotate slowly, half-submerged, orbiting one another in perfect, silent harmony. Their motion creates the illusion of a suspended sphere - whole, infinite, and impossibly precise. Each rotation sends faint ripples of light across the chamber, and with every pulse, the cables connected to the towering figure thrum in response.

	Out of the corner of your eyes someone - or something - approaches you:

	"He does not talk - we are all connected to his mind..."
\end{DndReadAloud}
\vfill\eject
{\noindent\entryfont This is the Robot Prince of Auchtertool, ruler-by-proxy and public face of the Robot Lordship. Unlike the Mecha-Lord, the Prince is mobile, articulate, and deliberately personable - designed as the interface between the mechanized seat of power and the mortal world.

The Robot Prince already suspects the party's importance. Prior to their arrival, Auchtertool received a fragmented but urgent distress transmission from Prince Angus McFife, reporting that Dundee has been completely obliterated by an overwhelming evil force. The message strongly implies that the Kingdom of Fife - and indeed all of Caledonia - now face an existential, possibly apocalyptic threat. Based on the nature of that message and the party's arrival at the very heart of Auchtertool, the Robot Prince reasonably concludes that the adventurers are a capable and battle-hardened unit.

Despite this, when the party inevitably seeks aid - whether military, technological, or arcane - the Robot Prince refuses to commit resources. His refusal is not dismissive or hostile; rather, it is calculated and strained. Auchtertool is currently facing an internal crisis:}

\begin{DndQuestHook}[width=0.5\textwidth - 4pt]{Never-Ending Nightmare}
	\DndQuestHookBasics[%
		location = {Cathedral of Auchtertool},%
		quest-giver = {Robot Prince of Auchtertool},%
		objective = {Defeat the Dread-Witch Queen of Cellardyke}%
	]%	
	{\noindent\entryfont A new and immediate threat has arisen near Auchtertool: the Dread-Witch Queen of Cellardyke, a powerful sorceress who has discovered a way to cripple constructs through nightmare-inducing magic. She can force automatons and warforged into a sleep-like state, subjecting them to arcane nightmares that destabilize their cores and siphon their animating soul-essence when they fail. This makes purely mechanical forces uniquely vulnerable to her influence.

	The Witch Queen has established herself in Ravenscraig Castle, near Kilkenny, along the shores of the Forth of Fife. From there, she is steadily expanding her influence toward Auchtertool.

	The Mecha-Lord and the Robot Prince attempted to eliminate her using a strike force of advanced constructs, but the assault failed. Ravenscraig Castle is now encircled by growing numbers of Undead known as Dreamers, animated by the Witch Queen and driven by endless nightmares. Previous attacks were repelled by sheer numbers before reaching the castle itself.\\\\
	For further information on the Dread-Witch Queen and her hideout in Ravenscraig Castle see the following \hyperref[quest:DreadWitchQueen]{\LinkFont{Queen of Nightmares Section}}.}
	
	\DndQuestRewards{Upon successfully defeating and apprehending the Dread-Witch Queen of Cellardyke, the party is rewarded with the following:}{%
		{Allegiance for Final Fight}{The Robot Prince of Auchtertool pledges allegiance to the party and the Kingdom of Fife to defeat the Evil Sorcerer Zargothrax.}%
	}
\end{DndQuestHook}

\section*{Gadget Shop}\phantomsection\addcontentsline{toc}{section}{Gadget Shop}

\subsection*{Shop Inventory}
\begin{DndTable}[header=Shop Inventory]{llR}
	Magic Item						& Rarity	& Price		\\
	Bracers of Defense				& Rare		& 4'000 GP	\\
	Clockwork Amulet				& Common	& 250 GP	\\
	Driftglobe						& Uncommon	& 500 GP	\\
	Eyes of Minute Seeing			& Uncommon	& 500 GP	\\
	Pole of Angling					& Common	& 150 GP	\\
	Pole of Collapsing				& Common	& 150 GP	\\
	Prostethic Limb					& Common	& 200 GP	\\
	Robe of Useful Items			& Uncommon	& 750 GP	\\
	Sending Stones					& Uncommon	& 600 GP	\\
	Staff of Adornment*				& Common	& 175 GP	\\
	Boots of the Winding Path		& Uncommon	& 500 GP	\\
	Dazzling Quarterstaff			& Rare		& 5'000 GP	\\
	Manifold Tool					& Common	& 100 GP	\\
	Mind Sharpener					& Uncommon	& 750 GP	\\
	Potion of Healing (4x)			& Common	& 100 GP	\\
	Potion of Greater Healing (2x) & Uncommon	& 400 GP
\end{DndTable}
\begingroup
	\DndSetThemeColor[PhbLightGreen]
	\begin{DndComment}{Staff of Adornment}
		Two smaller \hyperref[mi:HeroicInspirationCog]{\LinkFont{Cogs}} and a \hyperref[mi:WondrousPlaceKey]{\LinkFont{Key}} are floating above the staffs tip. These are only perceivable and retrievable once this magic item is bought.
	\end{DndComment}
\endgroup

\subsection*{Large Construct Prototype}
\subsubsection*{Apparatus of Kwalish}
\subsubsection*{Mighty Servant of Leuk-o}

\section*{Queen of Nightmares}\phantomsection\addcontentsline{toc}{section}{Queen of Nightmares}\label{quest:DreadWitchQueen}
{\entryfont Reaching Ravenscraig Castle without assistance is effectively impossible. The surrounding territory is saturated with roaming \hyperref[monster:Dreamer]{\LinkFont{Dreamers}}, layered patrol routes, and necromantic wards that continuously draw undead toward living - or animated - targets. Any small, unassisted group attempting to approach the castle will be detected and overwhelmed long before reaching the outer grounds.

To make the assault viable, the party must coordinate with the robot forces of Auchtertool. The Robot Prince of Auchtertool commits a contingent of warforged soldiers and heavy constructs, fully aware of the risks posed by the Dread-Witch Queen's magic. Their presence is not optional; it is the only way to create a breach in the Dreamer-controlled perimeter.

At this point, the party is presented with a strategic choice:
\begin{itemize}
	\item Fight alongside the Robot Allies
	\item Use the robots as a Distraction
\end{itemize}
To maintain narrative momentum and avoid a prolonged mass-combat encounter, the outcome of the assault can be abstracted into a short resolution sequence. The cumulative number of successes across all three rounds determines the overall outcome of the assault and the numbers of robots surviving which is used later in this quest, as well as a basis of the Strength of the robot army in the Final Battle, using the outcome table provided.}

\subsection*{Party Fights along Robot Allies}
{\entryfont The party joins the main assault, engaging the Dreamers head-on as the constructs push toward the castle. This approach is direct, chaotic, and costly, but allows the party to protect key constructs and influence the battlefield.

If this approach is chosen, the Dread-Witch Queen cannot be surprised when encountered and she will also have prepared some Ward-Traps in the boss room.}
\subsubsection*{Rolls per Round}
{\entryfont At the beginning of each round, the DM rolls one d20 and adds the Dreamers' Constitution modifier of \textbf{+3} to represent the resilience and relentless advance of the undead forces. Each player then rolls one d20 and adds a single preferred attack modifier. This modifier is chosen at the start of the sequence and remains the same for all three rounds, representing sustained contribution rather than individual tactical choices. Strength is appropriate for melee combatants, Dexterity for ranged fighters, and Intelligence or another spellcasting ability for casters.}
\subsubsection*{Determining Success and Failure}
{\entryfont A player is considered successful in a round if their total roll meets or exceeds the Dreamer roll for that round. The DM counts the number of successful player rolls each round, and the total number of successes across all three rounds determines the overall outcome of the assault, using the resolution table provided later in the quest.

If, in any round, all players fail to meet the Dreamer roll, the party suffers immediate consequences. Each character takes damage equal to the value indicated in the outcome table for that tier, reflecting moments where the line collapses, constructs are torn apart nearby, or the party is briefly overwhelmed by the psychic pressure of the Dreamers' nightmare-fuelled assault.}
\subsubsection*{Outcome (4 Players example)}
{\entryfont The players cannot be defeated in this battle, however, if the party rolls too poorly they will be forced to retreat and try on another day.}
\begin{DndTable}{lXXX}
	Outcome			& Level 4	& Level 5	& Level 6+	\\
	Full Fail Round	& 1d8 N		& 1d10 N	& 1d12 N	\\
	12-9 Successes	& 100\%		& 75\%		& 50\%		\\
	8-4 Successes	& 50\%		& 50\%		& 0\%		\\
	3-2 Successes	& 0\%		& 0\%		& Retreat	\\
	1-0 Successes	& 0\%		& Retreat	& Retreat	\\
\end{DndTable}

\subsection*{Robot Allies are Distraction}
{\entryfont If the party chooses to let the robot forces of Auchtertool fight alone while they infiltrate Ravenscraig Castle, the external battle is resolved in parallel with the confrontation against the Dread-Witch Queen, without drawing focus away from the interior scenes.}

\subsubsection*{Rolls per Round}
{\entryfont At the start of each round of the battle against the Dread-Witch Queen, the outside conflict is also advanced. For this resolution, a maximum of three rolls are made per round, shared between the DM and the players. The DM rolls one d20 and adds the Dreamers' Constitution modifier of +3, representing the endurance and swelling numbers of the undead host. The players collectively roll d20s - up to a maximum of three rolls per round - and each of these rolls adds the robot forces' Attack Bonus of +4, reflecting the disciplined but vulnerable warforged assault.}

\subsubsection*{Determining Success and Failure}
{\entryfont Each player roll that meets or exceeds the DM's Dreamer roll counts as a success. The number of successes accumulated over the course of the fight determines how effectively the robot forces thin the Dreamer ranks while the party operates inside the castle.}
\subsubsection*{Outcome (4 Players example)}
{\entryfont If the players roll poorly and achieve few successes, the robot forces fail to fully contain the undead. In this case, a significant number of Dreamers remain active when the party attempts to exit Ravenscraig Castle, immediately attacking the party on sight and turning the retreat into a dangerous secondary encounter.}
\begin{DndTable}{lXXX}
	Outcome			& Level 4		& Level 5		& Level 6+		\\
	Full Fail Round	& nothing		& +1 Dreamer	& +2 Dreamer	\\
	12-8 Successes	& 75\%			& 50\%			& 25\%			\\
	7-5 Successes	& 50\%			& 1 Dreamer		& 1 Dreamer		\\
	4-2 Successes	& 1 Dreamer		& 1 Dreamer		& 1 Dreamer		\\
	1-0 Successes	& 2 Dreamers	& 2 Dreamers	& 2 Dreamers	\\
\end{DndTable}

\subsection*{A Nightmarish Encounter}
\begin{DndTable}[header=Encounter Table]{XXX}
	Level 4				& Level 5			& Level 6		\\
	2 Animated Armor	& 3 Animated Armor	& 1 Conjurer	\\
						& 1 Cambion			& 1 Basilisk
\end{DndTable}

\begin{DndTrap}[width=0.5\textwidth - 4pt]{Necrotic Ward Trap}
	\DndTrapBasics[
		save_dc			= 15,
		skill			= {Dexterity Saving Throw},
		pos_reaction	= {-},
		neg_reaction	= {-},
		damage			= {5d6 Necrotic},
	]
	{\entryfont\noindent Each creature in a 10-foot radius must succeed on the Saving Throw}
\end{DndTrap}

\subsection*{Rewards}
{\entryfont After defeating the Dread-Witch Queen the party can be rewarded with the following treasures (Arcana-themed treasure hoard):
\begin{itemize}
	\item Amulet of Proof against Detection and Location
	\item Hag Eye
	\item Mystery Key
	\item Black Pearl (500 GP)
	\item Fire Opal (1'000 GP)
	\item 8 Potions of Greater Healing
	\item 1'000 GP in coins
\end{itemize}

\begingroup
	\DndSetThemeColor[PhbLightGreen]
	\begin{DndComment}{Mystery Key}
		\textit{Wondrous Item, common}\\
		A question mark is worked into the head of this key. The key has a 5 percent chance of unlocking any lock into which it's inserted. Whenever it fails to open a lock this chance is increased by 5 percent. Once it unlocks something, the key disappears.
	\end{DndComment}
\endgroup
}