% ------------------------------------------------------------------------------------------------------------- %
% #+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+# %
% ------------------------------------------------------------------------------------------------------------- %
%									MONSTER STAT BLOCK - TwoColumn // Long Name									%
% ------------------------------------------------------------------------------------------------------------- %
% #+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+#+# %
% ------------------------------------------------------------------------------------------------------------- %
\begin{DndMonster}[width=\textwidth + 8pt]{Blank Monster with a Long Name} % Name of Monster / Creature
	\begin{multicols}{2}
		\DndMonsterType{Unidentified Monster, unaligned}
		
		% Monster Basic Stats
		\DndMonsterBasics[
			armor-class = {10},
			hit-points  = {\DndDice{1d12 + 6}},
			speed       = {30 ft., Climb 25 ft.},
			initiative	= +3,
		]
		
		\renewcommand{\AbilityScoreSpacer}{~} % needed so it displays correctly
		
		% Monster Ability Scores
		\DndMonsterAbilityScores[
			str = 10,
			dex = 12,
			con = 8,
			int = 14,
			wis = 6,
			cha = 16,
		]
		
		% Monster Proficiencies, Vulnerabilities, Resistances, Immunities, Senses, Languages, CR, and Proficiency Bonus
		\DndMonsterDetails[
			saving-throws			= {STR +0, DEX +0, CON +5, INT +5, WIS -5},
			skills					= {Acrobatics +3, Stealth -3},
			damage-vulnerabilities	= {Cold},
			damage-resistances		= {Fire, Lightning},
			damage-immunities		= {Poison},
			condition-immunities	= {Frightened, Poisoned},
			gear					= {a mysterious item},
			senses					= {Darkvision 60 ft., Passive Perception 14},
			languages				= {Common, Abyssal},
			challenge				= 6, % XP are calculated automatically; can be omitted to display "-"
			proficiency-bonus		= +3, % default value +2
		]
		
		\DndMonsterSection{Traits}
		\DndMonsterAction{One of Many}
		The Blank Monster has advantage against being detected and on hiding in large groups.
		
	    \DndMonsterAction{Legendary Resistance (3 / Day)}
	    If the Blank Monster fails a saving throw, it can choose to succeed instead.
		
		\DndMonsterSection{Actions}
		\DndMonsterAction{Multiattack}
		The Blank Monster makes two attacks with its dagger.
		
		\DndMonsterAttack[
			name			= Longsword,
			distance		= melee,	% valid options are in the set {both,melee,ranged},
%			type			= weapon,	% valid options are in the set {weapon,spell}
			mod				= +3,
			reach			= 10,
%			range			= 20/60,
			targets			= one target,
			dmg				= \DndDice{1d8 + 2},
			dmg-type		= Slashing,
%			plus-dmg		= \DndDice{1d6},
%			plus-dmg-type	= Poison,
			or-dmg			= \DndDice{1d10 + 2},
			or-dmg-when		= {if used with two hands},
%			extra			= {. },
		]
		
		\DndMonsterAttack[
			name			= Poisoned Dagger,
			distance		= both,		% valid options are in the set {both,melee,ranged},
%			type			= weapon,	% valid options are in the set {weapon,spell}
			mod				= +5,
			reach			= 10,
			range			= 20/60,
			targets			= one target,
			dmg				= \DndDice{1d8 + 2},
			dmg-type		= Piercing,
			plus-dmg		= \DndDice{1d6},
			plus-dmg-type	= Poison,
%			or-dmg			= \DndDice{1d10},
%			or-dmg-when		= {},
%			extra			= {. },
	    ]
	    
		\DndMonsterAttack[
			name			= Longbow of Fate,
			distance		= ranged,	% valid options are in the set {both,melee,ranged},
%			type			= weapon,	% valid options are in the set {weapon,spell}
			mod				= +5,
%			reach			= 10,
			range			= 150/450,
			targets			= one target,
			dmg				= \DndDice{1d8 + 2},
			dmg-type		= Piercing,
%			plus-dmg		= \DndDice{1d6},
%			plus-dmg-type	= Poison,
%			or-dmg			= \DndDice{1d10 + 2},
%			or-dmg-when		= {if used with two hands},
			extra			= {. Critically hits the target on rolls of 19 and 20},
	    ]
	    
	    \DndMonsterSavingThrowEffect[%
	    	name = {Poison Cloud},
	    	description = {The creature releases a poisonous cloud from its body}, % can be omitted
	    	save_skill = {Constitution},
	    	save_dc = {15},
	    	targets = {all creatures within a 50 feet Emanation originating from the Blank Monster},
	    	failure = {The target has the Poisoned condition for 1 minute},
	    	success = {The target is not Poisoned}, % can be omitted
	    	extra={Any Poisoned creature takes \DndDice{1d6} Poison damage at the start of its turn} % can be omitted
	    ]
	    
	    \DndMonsterSection{Spells}
		\begin{DndMonsterSpells}
			\item[Innate Spellcasting] The Blank Monster Innate Spellcasting ability is Charisma (Spell Save DC 15). She can innately cast the following spells, requiring no material components:
			\DndInnateSpellLevel{At-Will Spell}
			\DndInnateSpellLevel[1]{Once-Per-Day Spells}
		\end{DndMonsterSpells}
		
		\begin{DndMonsterSpells}
			\item[Spellcasting] The Blank Monster can cast the following spells using Wisdom as the spellcasting ability (spell save DC 14, +6 to hit with spell attacks):
			\DndMonsterSpellLevel{Cantrip Spells}
			\DndMonsterSpellLevel[1]{1st Level Spells}
			\DndMonsterSpellLevel[2][3]{2nd Level Spells}
			\DndMonsterSpellLevel[3][3]{3rd Level Spells}
			\DndMonsterSpellLevel[4][3]{4th Level Spells}
			\DndMonsterSpellLevel[5][2]{5th Level Spells}
		\end{DndMonsterSpells}
	    
	    \DndMonsterSection{Bonus Actions}
	    \DndMonsterAction{Cunning Action}
	    The Blank Monster can take one of the following actions as a Bonus Action: Dash, Disengage, or Hide.
	    
	    \DndMonsterSection{Reactions}
	    \DndMonsterReaction[
	    	name = {Retaliation},
	    	trigger = {A creature hits the Blank Monster with a melee attack},
	    	response = {The Blank Monster can make an attack against that creature}
	    ]
	    
	    \DndMonsterSection{Legendary Actions}
	    The Blank Monster can take 3 legendary actions, choosing from the options below. Only one legendary action option can be used at a time and only at the end of another creature's turn. The Blank Monster regains spent legendary actions at the start of its turn.
		\begin{DndMonsterLegendaryActions}
			\DndMonsterLegendaryAction{Detect}{The Blank Monster makes a Wisdom (Perception) check.}
			\DndMonsterLegendaryAction{Attack}{The Blank Monster makes a Longsword attack.}
			\DndMonsterLegendaryAction{Barrage (Costs 2 Actions)}{The Blank Monster makes two Longbow attacks.}
		\end{DndMonsterLegendaryActions}
	\end{multicols}
\end{DndMonster}