\begin{DndMonster}[width=\textwidth + 8pt]{Angus McFife}
	\vspace*{-17.5pt}\begin{multicols}{2}
		\DndMonsterType{Human Fighter (Lvl 7, Battle Master), lawful good}
		
		% If you want to use commas in the key values, enclose the values in braces.
		\DndMonsterBasics[
			armor-class = {16 (Studded Leather Armor)},
			hit-points  = {\DndDice{7d10 + 14}},
			speed       = {30 ft.},
		]
		
		\renewcommand{\AbilityScoreSpacer}{~}
		\DndMonsterAbilityScores[
			str = 14,
			dex = 18,
			con = 14,
			int = 10,
			wis = 12,
			cha = 16,
		]
		
		\DndMonsterDetails[
			saving-throws = {STR +4, Con +5},
			skills = {Animal Handling +4, Acrobatics +7, History +3, Insight +4, Nature +3, Perception +4, Performance +6, Persuasion +6, Stealth +7},
			%damage-vulnerabilities = {cold},
			%damage-resistances = {bludgeoning, piercing, and slashing from nonmagical attacks},
			%damage-immunities = {poison},
			senses = {Passive Perception 14},
			%condition-immunities = {poisoned},
			languages = {Common},
			challenge = -,
			proficiency-bonus=+3
		]
		
		\DndMonsterSection{Traits}	
	    \DndMonsterAction{Musician}
	    During a Short or Long Rest Angus McFife can give up to 3 allies an Heroic Inspiration.
		
		\DndMonsterAction{Great Weapon Fighting}
		When Angus rolls damage for an attack he makes with a Melee weapon that he is holding with two hands, he can treat any 1 or 2 on a damage die as a 3. The weapon must have the Two-Handed or Versatile property to gain this benefit.
		
		\DndMonsterAction{Action Surge (1 use per SR or LR)}
		Angus McFife can take an additional action during his turn.
		
		\DndMonsterAction{Combat Superiority}
		Angus McFife has 5 Superiority Dice (d8) which he can use to do his maneuvers. He regains all expended Superiority Dice when he finishes a Short or Long Rest.
		
		\DndMonsterAction{Commanding Presence}
		When Angus McFife makes a Charisma (Intimidation, Performance, or Persuasion) check he can add one Superiority Die to the roll.
		
		\DndMonsterAction{Trip Attack}
		When Angus McFife hits a creature with an attack, he can expend a Superiority Dice and add it to the damage roll. If the target is Large or smaller, it must succeed on a Strength Saving Throw (DC 15) or be knocked prone.
		
		\DndMonsterSection{Actions}
		\DndMonsterAction{Extra Attack}
		Angus McFife can attack twice whenever he takes the Attack Action.
		
		\DndMonsterAction{Commander's Strike}
		When Angus McFife takes the Attack Action he can forego his attack to command another companion to strike. That creature takes its Reaction to make an attack, adding the Superiority Die to the attack's damage roll on a hit.
		
		\DndMonsterAttack[
			name=Scimitar,
			distance=melee, % valid options are in the set {both,melee,ranged},
			%type=weapon, %valid options are in the set {weapon,spell}
			mod=+7,
			reach=5,
			%range=20/60,
			targets=one target,
			dmg=\DndDice{1d6 + 4},
			dmg-type=slashing,
			%plus-dmg=\DndDice{1d6},
			%plus-dmg-type=poison,
			or-dmg=\DndDice{1d10 + 5},
			or-dmg-when={when used with two hands},
			extra={. When Angus McFife makes an extra attack using the Scimitar hec an do so as part of the Attack action instead of using the Bonus Action},
		]
		
		\DndMonsterAttack[
			name=Shortsword,
			distance=melee, % valid options are in the set {both,melee,ranged},
			%type=weapon, %valid options are in the set {weapon,spell}
			mod=+7,
			reach=5,
			%range=20/60,
			targets=one target,
			dmg=\DndDice{1d6 + 4},
			dmg-type=piercing,
			%plus-dmg=\DndDice{1d6},
			%plus-dmg-type=poison,
			%or-dmg=,
			%or-dmg-when=,
			extra={. When Angus hits a creature with this weapon he gains Advantage on the next attack roll against that creature},
		]
		
		\DndMonsterAttack[
			name=Longbow,
			distance=ranged, % valid options are in the set {both,melee,ranged},
			%type=weapon, %valid options are in the set {weapon,spell}
			mod=+7,
			%reach=5,
			range=150/600,
			targets=one target,
			dmg=\DndDice{1d8 + 4},
			dmg-type=piercing,
			%plus-dmg=\DndDice{1d6},
			%plus-dmg-type=poison,
			%or-dmg=,
			%or-dmg-when=,
			extra={. A creature hit with this attack has its speed reduced by 10 feet, up to a maximum reduction of 10 feet},
		]
		
		\DndMonsterSection{Bonus Action}
		\DndMonsterAction{Second Wind (3 charges)}
		Angus McFife regains \DndDice{1d10 + 7} Hit Points. Also he can move up to half his speed without provoking Opportunity Attacks.
		
		\DndMonsterAction{Rally}
	    Angus McFife bolsters the resolve of a creature. By expending one Superiority Die that creature gains \DndDice{1d8 + 3} Temporary Hit Points.
		
		\DndMonsterSection{Reaction}
		\DndMonsterAction{Riposte}
		When a creature misses Angus McFife he can expend a Superiority Die to immediately attack that creature adding the Superiority Die to the attack's damage roll on a hit.
	\end{multicols}
\end{DndMonster}