\begin{DndMonster}[width=0.5\textwidth]{Alasdair MacLeod}
	\DndMonsterType{Goliath (Stone) Barbarian, Neutral}
	
	% If you want to use commas in the key values, enclose the values in braces.
	\DndMonsterBasics[
		armor-class = {16 (Natural Armor)},
		initiative	= +1,
		hit-points  = {\DndDice{1d12 + 4}},
		speed       = {35 ft.},
	]
	
	\renewcommand{\AbilityScoreSpacer}{~}
	\DndMonsterAbilityScores[
		str = 18,
		dex = 13,
		con = 15,
		int = 10,
		wis = 12,
		cha = 8,
	]
	
	\DndMonsterDetails[
		saving-throws			= {STR +6, CON +4},
		skills					= {Athletics +6, Animal Handling +3, Survival +3},
%		damage-vulnerabilities	= {Cold},
%		damage-resistances		= {Bludgeoning, Piercing, and Slashing from nonmagical attacks},
%		damage-immunities		= {Poison},
%		condition-immunities	= {Poisoned},
%		gear					= {Leather Armor, Light Crossbow, Scimitar},
		senses					= {Passive Perception 11},
		languages				= {Common, Giant},
%		challenge				= -,
%		proficiency-bonus		= +2,
	]
    
	\DndMonsterSection{Traits}
	\DndMonsterAction{Powerful Build}
	Alasdair has Advantage on any saving throw he makes to end the Grappled condition. He also counts as one size larger when determining his carrying capacity.
	
	\DndMonsterAction{Rage}
	While the Rage is active, Alasdair gains the following benefits:
	\begin{itemize}
		\item He has resistance against bludgeoning, slashing, and piercing damage
		\item When he makes an attack using Strength, his damage increases by +2
		\item He has advantage on Strength checks and Strength saving throws
	\end{itemize}
	
	\DndMonsterSection{Actions}
	\DndMonsterAttack[
		name			= Battleaxe,
		distance		= melee,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +6,
		reach			= 5,
%		range			= 20/60,
		targets			= one target,
		dmg				= \DndDice{1d8 + 4},
		dmg-type		= Slashing,
%		plus-dmg		= \DndDice{1d6},
%		plus-dmg-type	= Poison,
		or-dmg			= \DndDice{1d10 + 4},
		or-dmg-when		= {when used with two hands},
%		extra			= {},
	]
	
	\DndMonsterAttack[
		name			= Shortbow,
		distance		= ranged,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +3,
%		reach			= 5,
		range			= 80/320,
		targets			= one target,
		dmg				= \DndDice{1d6 + 1},
		dmg-type		= Piercing,
%		plus-dmg		= \DndDice{1d6},
%		plus-dmg-type	= Poison,
%		or-dmg			= \DndDice{1d20},
%		or-dmg-when		= {},
%		extra			= {},
	]
	
	\DndMonsterSection{Bonus Actions}
	\DndMonsterAction{Rage (2 / Short or Long Rest)}
	Alasdair can enter a Rage while he is not wearing Heavy Armor. He will gain all Rage benefits and it lasts until the end of his next turn if he does not extend it. He can maintain the Rage for up to 10 minutes.
	
	\DndMonsterSection{Reactions}
	\DndMonsterAction{Stone's Endurance (2 / Long Rest)}
    When Alasdair takes damage, he can take a Reaction to roll 1d12. Add his Constitution modifier to the number rolled and reduce the damage by the total.
\end{DndMonster}