\begin{DndMonster}[width=0.5\textwidth]{Gavin Buchanan}
	\DndMonsterType{Halfling Rogue, Chaotic Neutral}
	
	% If you want to use commas in the key values, enclose the values in braces.
	\DndMonsterBasics[
		armor-class = {15 (Leather Armor)},
		initiative	= +4,
		hit-points  = {\DndDice{2d10 + 4}},
		speed       = {30 ft.},
	]
	
	\renewcommand{\AbilityScoreSpacer}{~}
	\DndMonsterAbilityScores[
		str = 9,
		dex = 18,
		con = 14,
		int = 15,
		wis = 13,
		cha = 12,
	]
	
	\DndMonsterDetails[
		saving-throws			= {DEX +6, INT +4},
		skills					= {Acrobatics +6, Perception +5, Stealth +8},
%		damage-vulnerabilities	= {Cold},
%		damage-resistances		= {Bludgeoning, Piercing, and Slashing from nonmagical attacks},
%		damage-immunities		= {Poison},
%		condition-immunities	= {Poisoned},
%		gear					= {Leather Armor, Light Crossbow, Scimitar},
		senses					= {Passive Perception 15},
		languages				= {Common, Thieves' Cant},
%		challenge				= -,
%		proficiency-bonus		= +2,
	]
    
	\DndMonsterSection{Traits}
	\DndMonsterAction{Brave}
	Gavin has Advantage on saving throws he makes to avoid or end the Frightened condition.
	
	\DndMonsterAction{Halfling Nimbleness}
	Gavin can move through the space of any creature that is a size larger than him, but he can't stop in the same space.
	
	\DndMonsterAction{Luck}
	When Gavin rolls a 1 on the d20 of a D20 Test, he can reroll the die, and he must use the new roll.
	
	\DndMonsterAction{Naturally Stealthy}
	Gavin can take the Hide action even when he is obscured only by a creature that is at least one size larger than him.
	
	\DndMonsterAction{Sneak Attack}
	Once per turn, Gavin can deal an extra 2d6 damage to one creature he hits with an attack roll if he has Advantage on the roll and the attack uses a Finesse or Ranged weapon. The extra damage's tyoe is the same as the weapon's type.
	
	\DndMonsterAction{Steady Aim}
	If Gavin hasn't moved during his turn, he can give himself Advantage on his next attack on the current turn. After he uses it, his Speed is 0 until the end of the current turn.
	
	\DndMonsterSection{Actions}
	\DndMonsterAttack[
		name			= Dagger,
		distance		= melee,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +6,
		reach			= 5,
%		range			= 20/60,
		targets			= one target,
		dmg				= \DndDice{1d4 + 4},
		dmg-type		= Piercing,
%		plus-dmg		= \DndDice{1d6},
%		plus-dmg-type	= Poison,
%		or-dmg			= \DndDice{1d20},
%		or-dmg-when		= {},
%		extra			= {},
	]
	
	\DndMonsterAttack[
		name			= Shortbow,
		distance		= ranged,	% valid options are in the set {both,melee,ranged}
		%type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +6,
		%reach			= 5,
		range			= 80/320,
		targets			= one target,
		dmg				= \DndDice{1d6 + 4},
		dmg-type		= Piercing,
		%plus-dmg		= \DndDice{1d6},
		%plus-dmg-type	= Poison,
		%or-dmg			= \DndDice{1d20},
		%or-dmg-when	= {},
		%extra			= {},
	]
	
	\DndMonsterSection{Spells}
	\begin{DndMonsterSpells}
		\item[Spellcasting] Gavin Buchanan can cast the following spells using Intelligence as the spellcasting ability (spell save DC 12, +4 to hit with spell attacks):
		\DndMonsterSpellLevel{Mage Hand, Mind Sliver, Minor Illusion}
		\DndMonsterSpellLevel[1][2]{Disguise Self, Fog Cloud, Long Strider}
	\end{DndMonsterSpells}
	
	\DndMonsterSection{Bonus Actions}
	\DndMonsterAction{Cunning Action}
	Gavin can take one of the following actions as a Bonus Action: Dash, Disengage, or Hide.
\end{DndMonster}