\begin{DndMonster}[width=\textwidth + 8pt]{Zargothrax} % Acererak
	\vspace*{-17.5pt}\begin{multicols}{2}
		\DndMonsterType{Medium Undead, Chaotic Evil}
		
		% If you want to use commas in the key values, enclose the values in braces.
		\DndMonsterBasics[
			armor-class = {21 (Natural Armor)},
			initiative	= +3,
			hit-points  = {\DndDice{30d8 + 150}},
			speed       = {30 ft.},
		]
		
		\renewcommand{\AbilityScoreSpacer}{~}
		\DndMonsterAbilityScores[
			str = 13,
			dex = 16,
			con = 20,
			int = 27,
			wis = 21,
			cha = 20,
		]
		
		\DndMonsterDetails[
			%saving-throws			= {CON +8, CHA +9},
			skills					= {Arcana +22, History +22, Insight +12. Perception +12},
			%damage-vulnerabilities	= {cold},
			damage-resistances		= {Cold, Lightning},
			damage-immunities		= {Bludgeoning, Piercing, and Slashing damage from nonmagical attack, Necrotic, Poison},
			condition-immunities	= {Blinded, Charmed, Deafened, Exhaustion, Frightened, Paralyzed, Petrified, Poisoned, Stunned},
%			gear					= {Leather Armor, Light Crossbow, Scimitar},
			senses					= {Truesight 120 ft., Passive Perception 22},
			languages				= {Abyssal, Common, Draconic, Dwarvish, Elvish, Giant, Infernal, Primordial, Undercommon},
			challenge				= 23,
			proficiency-bonus		= +7,
		]
		
		\DndMonsterSection{Traits}
		\DndMonsterAction{Legendary Resistance (3/Day)}
		If Zargothrax fails a saving throw, he can choose to succeed instead.
		
		\DndMonsterAction{Turn Resistance}
		Zargothrax has advantage on saving throws against any effect that turns undead.
		
		\DndMonsterSection{Actions}
		\DndMonsterAttack[
			name			= Knife of Evil,
			distance		= melee,	% valid options are in the set {both,melee,ranged}
			%type			= weapon,	% valid options are in the set {weapon,spell}
			mod				= +11,
			reach			= 5,
			%range			= 20/60,
			targets			= one target,
			dmg				= \DndDice{1d4 + 4},
			dmg-type		= Piercing,
			%plus-dmg		= \DndDice{1d6},
			%plus-dmg-type	= Poison,
			%or-dmg			= \DndDice{1d20},
			%or-dmg-when	= {},
			%extra			= {},
		]
		
		\DndMonsterAttack[
			name			= Paralyzing Touch,
			distance		= melee,	% valid options are in the set {both,melee,ranged}
			type			= spell,	% valid options are in the set {weapon,spell}
			mod				= +15,
			reach			= 5,
%			range			= 20/60,
			targets			= one target,
			dmg				= \DndDice{3d6},
			dmg-type		= Cold,
%			plus-dmg		= \DndDice{1d6},
%			plus-dmg-type	= Poison,
%			or-dmg			= \DndDice{1d20},
%			or-dmg-when		= {},
			extra			= {, and the target must succeed on a DC 20 Constitution saving throw or be paralyzed for 1 minute. The target can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success},
		]
		
		\DndMonsterSection{Spells}
		\begin{DndMonsterSpells}
			\item[Spellcasting] Zargothrax is a 20th-level spellcaster. His spellcasting ability is Intelligence (spell save DC 23, +15 to hit with spell attacks). Zargothrax has the following wizard spells prepared:
			\DndMonsterSpellLevel[Cantrips][At will]{Mage Hand, Ray of Frost, Shocking Grasp}
			\DndMonsterSpellLevel[1][At will]{Ray of Sickness, Shield}
			\DndMonsterSpellLevel[2][At will]{Arcane Lock, Knock}
			\DndMonsterSpellLevel[3][At will]{Animate Dead, Counterspell}
			\DndMonsterSpellLevel[4][3]{Blight, Ice Storm, Phantasmal Killer}
			\DndMonsterSpellLevel[5][3]{Cloudkill, Hold Monster, Wall of Force}
			\DndMonsterSpellLevel[6][3]{Chain Lightning, Circle of Death, Disintegrate}
			\DndMonsterSpellLevel[7][3]{Finger of Death, Plane Shift, Teleport}
			\DndMonsterSpellLevel[8][2]{Maze, Mind Blank}
			\DndMonsterSpellLevel[9][2]{Power Word Kill, Time Stop}
		\end{DndMonsterSpells}
		
		\DndMonsterSection{Legendary Actions}
		Zargothrax can take 3 legendary actions, choosing from the options below. Only one legendary action can be used at a time and only at the end of another creature's turn. Zargothrax regains spent legendary actions at the start of its turn.
		\begin{DndMonsterLegendaryActions}
			\DndMonsterLegendaryAction{At-Will Spell}{Zargothrax cast one of his at-will spells.}
			\DndMonsterLegendaryAction{Melee Attack}{Zargothrax uses Paralyzing Touch or makes one melee attack with his Knife of Evil.}
			\DndMonsterLegendaryAction{Frightening Gaze (Costs 2 Actions)}{Zargothrax fixes his gaze on one creature he can see within 10 feet of him. The target must succeed on a DC 20 Wisdom saving throw against this magic or become frightened for 1 minute. The frightened target can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success. If a target's saving throw is successful or the effect ends for it, the target its immune to Zargothrax's gaze for the next 24 hours.}
			\DndMonsterLegendaryAction{Disrupt Life (Costs 3 Actions)}{Each creature within 20 feet of Zargothrax must make a DC 20 Constitution saving throw against this magic, taking 42 (12d6) necrotic damage on a failed save, or half as much damage on a successful one.}
		\end{DndMonsterLegendaryActions}
	\end{multicols}
\end{DndMonster}