\begin{DndMonster}[width=0.5\textwidth]{Ancestral Laserdragon}
	\DndMonsterType{Gargantuan Dragon, true neutral}
	
	% If you want to use commas in the key values, enclose the values in braces.
	\DndMonsterBasics[
		armor-class = {22 (Natural Armor)},
		initiative	= +7,
		hit-points  = {\DndDice{26d20 + 208}},
		speed       = {40 ft., burrow 40 ft., fly 80 ft.},
	]
	
	\renewcommand{\AbilityScoreSpacer}{~}
	\DndMonsterAbilityScores[
		str = 29,
		dex = 10,
		con = 27,
		int = 18,
		wis = 17,
		cha = 21,
	]
	
	\DndMonsterDetails[
		saving-throws			= {DEX +7, CON +15, WIS +10, CHA +12},
		skills					= {Perception +17, Stealth +7},
%		damage-vulnerabilities	= {Cold},
%		damage-resistances		= {Bludgeoning, Piercing, and Slashing from nonmagical attacks},
		damage-immunities		= {Lightning, Poison},
		condition-immunities	= {Poisoned},
%		gear					= {Leather Armor, Light Crossbow, Scimitar},
		senses					= {Blindsight 60 ft., Darkvision 120 ft., Passive Perception 27},
		languages				= {Common, Draconic},
		challenge				= 23,
		proficiency-bonus		= +7,
	]
	
	\DndMonsterSection{Traits}
    \DndMonsterAction{Legendary Resistance (3/Day)}
    If the dragon fails a saving throw, it can choose to succeed instead.
	
	\DndMonsterSection{Actions}
	\DndMonsterAction{Multiattack}
	The dragon can use its Frightful Presence. It then makes three attacks: one with its bite and two with its claws.
	
	\DndMonsterAttack[
		name			= Bite,
		distance		= melee,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +16,
		reach			= 15,
%		range			= 20/60,
		targets			= one target,
		dmg				= \DndDice{2d10 + 9},
		dmg-type		= Piercing,
		plus-dmg		= \DndDice{2d10},
		plus-dmg-type	= Lightning,
%		or-dmg			= \DndDice{1d20},
%		or-dmg-when		= {},
%		extra			= {},
	]
	
	\DndMonsterAttack[
		name			= Claw,
		distance		= melee,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +16,
		reach			= 10,
%		range			= 20/60,
		targets			= one target,
		dmg				= \DndDice{2d6 + 9},
		dmg-type		= Slashing,
%		plus-dmg		= \DndDice{1d6},
%		plus-dmg-type	= Poison,
%		or-dmg			= \DndDice{1d20},
%		or-dmg-when		= {},
%		extra			= {},
	]
	
	\DndMonsterAttack[
		name			= Tail,
		distance		= melee,	% valid options are in the set {both,melee,ranged}
%		type			= weapon,	% valid options are in the set {weapon,spell}
		mod				= +16,
		reach			= 20,
%		range			= 20/60,
		targets			= one target,
		dmg				= \DndDice{2d8 + 9},
		dmg-type		= Bludgeoning,
%		plus-dmg		= \DndDice{1d6},
%		plus-dmg-type	= Poison,
%		or-dmg			= \DndDice{1d20},
%		or-dmg-when		= {},
%		extra			= {},
	]
	
	\DndMonsterAction{Frightful Presence (Recharge 5-6)}
	Each creature of the dragon's choice that is within 120 feet of the dragon and aware of it must succeed on a DC 20 Wisdom saving throw or become frightened for 1 minute. A creature can repeat the saving throw at the end of each of its turns, ending the effect on itself on a success. If a creature's saving throw is successful or the effect ends for it, the creature is immune to the dragon's Frightful Presence for the next 24 hours.
	
	\DndMonsterAction{Lightning Breath (Recharge 5-6)}
	The dragon exhales lightning in a 120-­foot line that is 10 feet wide. Each creature in that line must make a DC 23 Dexterity saving throw, taking \DndDice{16d10} lightning damage on a failed save, or half as much damage on a successful one.
	
	\DndMonsterSection{Legendary Actions}
	The dragon can take 3 legendary actions, choosing from the options below. Only one legendary action option can be used at a time and only at the end of another creature's turn. The dragon regains spent legendary actions at the start of its turn.
	\begin{DndMonsterLegendaryActions}
		\DndMonsterLegendaryAction{Detect}{The dragon makes a Wisdom (Perception) check.}
		\DndMonsterLegendaryAction{Tail Attack}{The dragon makes a tail attack.}
		\DndMonsterLegendaryAction{Wing Attack (Costs 2 Actions)}{The dragon beats its wings. Each creature within 15 feet of the dragon must succeed on a DC 24 Dexterity saving throw or take \DndDice{2d6 + 9} bludgeoning damage and be knocked prone. The dragon can then fly up to half its flying speed.}
	\end{DndMonsterLegendaryActions}
\end{DndMonster}